Demo arXiv template

### 2022-10-19 paper/paper.qmd
tweaks and todo after today's meeting

**What is the problem with current index construction**

Currently, index construction lacks a standardised workflow. 
It is often up to researchers or research institutions to decide whether to provide open source code on the new indices, what would be the best user interface for other researchers to use the new indices, and how easily the new indices can be compared with other existing indices. 
This makes the computation lack transparency and indices cumbersome to experiment with.
Researchers who wish to validate the indices calculated from large institutes need to reinvent the wheels themselves since the source code used for computing is often not available for public consumption.
Open-source code provided by research groups has a narrow margin for exploring other options outside the provided.
Similar steps used by different indices are difficult to spot since the design of the user interface for indices often includes all the steps under a single function call.
And lastly, it is generally hard to inspect intermediate results during the index construction if users wish to check the output of a certain step.

@@

@@

*This week: need to extend each point of why it is beneficial further with more information?*

While every jumbled index jumbles in its own way, perspicuous indices are all alike. 
This paper proposes a data pipeline for index construction. 
By recognising the common steps shared by many indices, we develop a pipeline that breaks down index construction into multiple modules and allow operations in various modules to be combined like building blocks to construct indices.
The pipeline approach is general while adaptable to most index construction. 
It allows indices to be created, studied, and compared in a structured tidy form and enables statistical analysis of indices to be performed easily: 
More specifically, it enables researchers to 1) validate the indices calculated from external organisations, 2) unify various indices under the same framework for comparison, 3) swap or adjust individual steps in the index construction to study their contribution, 4) calculate uncertainty on indices through bootstrap or others, and finally, 5) inspire proposal of new indices from combining different steps in existing indices.

@@

This work could interests researchers actively developing new indices to deliver new indices in an easy-to-reproduce design. 
It would also provide analysts who wish to compute a range of indices in their analysis a uniform interface to build relevant indices from raw data. 
For statisticians and software developing engineers, this work frames the workflow of index construction and could motivate similar work in other workflow used in practice.

>>>>

**What is the challenges with current index construction**

Currently, index construction lacks a standardised workflow. 
It is often up to researchers or research institutions to decide whether to provide open source code on the new indices, what would be the best user interface for other researchers to use the new indices, and how easily the new indices can be compared with other existing indices. 
This makes the computation lack transparency and indices cumbersome to experiment with:

  - Researchers who wish to validate the indices calculated from large institutes need to reinvent the wheels themselves since the source code used for computing is often not available for public consumption;
  - Open-source code provided by research groups has a narrow margin for exploring other options outside the provided;
  - Similar steps used by different indices are difficult to spot since the design of the user interface for indices often includes all the steps under a single function call; and
  - It is generally hard to inspect intermediate results during the index construction if users wish to check the output of a certain step.

TODO: see if there is any paper describing this type of pains

@@

TODO: useful to reference tidy data and tidy model that makes the workflow on modelling tidy somewhere in introduction

@@

~~While every jumbled index jumbles in its own way, [perspicuous] clearly-laied out indices are all alike.~~
This paper proposes a data pipeline for index construction. 
By recognising the common steps shared by many indices, we develop a pipeline that breaks down index construction into multiple modules and allow operations in various modules to be combined like building blocks to construct indices.
The pipeline approach is general while adaptable to most index construction. 
It allows indices to be created, studied, and compared in a structured tidy form and enables statistical analysis of indices to be performed easily: 
More specifically, it enables researchers to 1) validate the indices calculated from external organisations, 2) unify various indices under the same framework for computing, 3) swap or adjust individual steps in the index construction to study their contribution, 4) calculate uncertainty on indices through bootstrap or others, 5) enhance existing indices through comparing and studying their statistical properties, and finally, 6) propose new indices from combining different steps in existing indices.

TODO: first sentence: tailor to their indices without thinking about the big picture

@@

This work is of interest to researchers actively developing new indices since it encourages new indices to be delivered in an easy-to-reproduce design. 
It would also provide analysts who wish to compute a range of indices in their analysis a uniform interface to build relevant indices from raw data. 
For statisticians and software developing engineers, this work frames the process of index construction in a more user-oriented workflow and could motivate similar research for other process in scientific computing.

### 2022-10-19 paper/paper.tex
tweaks and todo after today's meeting

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

\textbf{What is the problem with current index construction}

Currently, index construction lacks a standardised workflow. It is often
up to researchers or research institutions to decide whether to provide
open source code on the new indices, what would be the best user
interface for other researchers to use the new indices, and how easily
the new indices can be compared with other existing indices. This makes
the computation lack transparency and indices cumbersome to experiment
with. Researchers who wish to validate the indices calculated from large
institutes need to reinvent the wheels themselves since the source code
used for computing is often not available for public consumption.
Open-source code provided by research groups has a narrow margin for
exploring other options outside the provided. Similar steps used by
different indices are difficult to spot since the design of the user
interface for indices often includes all the steps under a single
function call. And lastly, it is generally hard to inspect intermediate
results during the index construction if users wish to check the output
of a certain step.

@@

\emph{This week: need to extend each point of why it is beneficial
further with more information?}

While every jumbled index jumbles in its own way, perspicuous indices
are all alike. This paper proposes a data pipeline for index
construction. By recognising the common steps shared by many indices, we
develop a pipeline that breaks down index construction into multiple
modules and allow operations in various modules to be combined like
building blocks to construct indices. The pipeline approach is general
while adaptable to most index construction. It allows indices to be
created, studied, and compared in a structured tidy form and enables
statistical analysis of indices to be performed easily: More
specifically, it enables researchers to 1) validate the indices
calculated from external organisations, 2) unify various indices under
the same framework for comparison, 3) swap or adjust individual steps in
the index construction to study their contribution, 4) calculate
uncertainty on indices through bootstrap or others, and finally, 5)
inspire proposal of new indices from combining different steps in
existing indices.

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\textbf{What is the challenges with current index construction}

Currently, index construction lacks a standardised workflow. It is often
up to researchers or research institutions to decide whether to provide
open source code on the new indices, what would be the best user
interface for other researchers to use the new indices, and how easily
the new indices can be compared with other existing indices. This makes
the computation lack transparency and indices cumbersome to experiment
with:

\begin{itemize}
\tightlist
\item
  Researchers who wish to validate the indices calculated from large
  institutes need to reinvent the wheels themselves since the source
  code used for computing is often not available for public consumption;
\item
  Open-source code provided by research groups has a narrow margin for
  exploring other options outside the provided;
\item
  Similar steps used by different indices are difficult to spot since
  the design of the user interface for indices often includes all the
  steps under a single function call; and
\item
  It is generally hard to inspect intermediate results during the index
  construction if users wish to check the output of a certain step.
\end{itemize}

TODO: see if there is any paper describing this type of pains

TODO: useful to reference tidy data and tidy model that makes the
workflow on modelling tidy somewhere in introduction

@@

\sout{While every jumbled index jumbles in its own way,
{[}perspicuous{]} clearly-laied out indices are all alike.} This paper
proposes a data pipeline for index construction. By recognising the
common steps shared by many indices, we develop a pipeline that breaks
down index construction into multiple modules and allow operations in
various modules to be combined like building blocks to construct
indices. The pipeline approach is general while adaptable to most index
construction. It allows indices to be created, studied, and compared in
a structured tidy form and enables statistical analysis of indices to be
performed easily: More specifically, it enables researchers to 1)
validate the indices calculated from external organisations, 2) unify
various indices under the same framework for computing, 3) swap or
adjust individual steps in the index construction to study their
contribution, 4) calculate uncertainty on indices through bootstrap or
others, 5) enhance existing indices through comparing and studying their
statistical properties, and finally, 6) propose new indices from
combining different steps in existing indices.

TODO: first sentence: tailor to their indices without thinking about the
big picture
